intro

### 2022-02-07 06_Paper/ER-ED/TheoreticalBackground.Rmd
made annotations

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies affects their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012]. 
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
With an effect size of _d~+~_ = 0.45 distancing as tactic of cognitive change showed the highest effectiveness [@Webb2012].
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on the general benefit, longer-term consequences must also be considered. 
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies to psychological disorders [@Aldao2010].

<!--CS: Mit dem Teil bin ich noch nciht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl. strukturieren kann! -->
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering in the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. 
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
People choose a strategy that they prefer, for different, relatively well-known reasons. 
However, nothing is revealed about the strategy that is not chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: a strategy is valued high if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are intercomputed by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal and is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual subjective values (SV) of effortful cognitive tasks have been quantified using the cognitive effort discounting paradigm (COG-ED) [@Westbrook2013].

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, We will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm."}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study

The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies. 
We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively more effortful than distraction and suppression.
Regarding SVs of ER strategies we expect that (3a) people choose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 
<!-- to specific ? to unspecific? -->

>>>>

Every day we are confronted with stressful or emotionally demanding situations. 
The ability to modify emotional experiences, expressions, and physiological reactions [@Gross1998antecedent] to regulate emotions is an important cognitive skill. 
It is therefore not surprising that emotion regulation (ER) has substantial implications for well-being and adaptive functioning [@Gross1998emerging].
Different strategies can be used to regulate emotions, namely situation selection, situation modification, attentional deployment, cognitive change, and response modification [@Gross1998antecedent], and, following the taxonomy of Powers and LaBar [-@Powers2019], individuals can implement ER strategies by means of different tactics.
So called antecedent-focused strategies, e.g., attentional deployment and cognitive change, take effect early in the emotion generation process [@Gross1998antecedent].
In contrast, response modification takes place late in the process and is therefore conceptualized as a response-focused strategy [@Gross1998antecedent].
This postulated temporal sequence of ER strategies influences their effectiveness.
It is meta-analytically proven that all mentioned strategies reduce subjective emotional arousal [@Webb2012].
<!--JZ: Das "on outcomes in measures" im folgenden Satz klingt doppelt gemoppelt, das sollte vielleicht noch umformuliert werden -->
Distraction as a tactic of attentional deployment and (expressive) suppression as a tactic of response modulation showed small to medium effect sizes on outcomes in measures of emotional experience (distraction: _d~+~_ = 0.27; suppression: _d~+~_ = 0.27).
Distancing as tactic of cognitive change showed the highest effectiveness with an effect size of _d~+~_ = 0.45 [@Webb2012].
So these tactics from three different strategies proved to be effective in the short term. 
However, in order to be able to make a statement on their general benefit, longer-term consequences must also be considered. 
Especially strategies that do not put the emotional content of the situation into a neutral perspective (i.e., distraction and suppression) are presumed to be disadvantageous in the longer term.
Long-term consequences of subjectively reported habitual use of emotion regulation strategies for affect and well-being have been discussed [@GrossJohn2003]. 
Especially suppression is generally associated with poorer outcomes (i.e., more negative affect, lower general well-being), which led to the assumption of *adaptive* and *maladaptive* strategies.
For example, it could be shown that maladaptive ER strategies mediate the effect between neuroticism and depressive symptoms [@Yoon2013].
Also, meta-analytic evidence exists linking a number of ER strategies to psychological disorders [@Aldao2010]. <!--JZ: Oben formulierst du es als "meta-analytically proven", dass das Arousal reduziert wird, hier als "meta-analytic evidence exists" für den Zsmh mit Disorders; ich finde, man sollte beiden Metaanalysen die gleiche Evidenzstärke zusprechen; macht das Sinn?-->

<!--CS: Mit dem Teil bin ich noch nciht ganz zufrieden, freue mich über Anmerkungen, wie man das evtl. strukturieren kann! -->
The postulation of *adaptive* and *maladaptive* strategies was put in a new perspective with the concept of ER flexibility.
Similar to other psychological domains, e.g., attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
First, adaptive flexible ER requires having a large repertoire of ER strategies [@Aldao2015]. <!--JZ: Hier mit "First" weiterzumachen, ist nicht so sinnvoll, weil der vorherige Satz keine Argumentation einleitet, die nun durch first, second, etc. ausgeführt werden soll-->
For example, greater ER variability is related to reduced negative affect and therefore beneficial in daily life [@Blanke2020].
Second, strategies have to be chosen from the repertoire that are useful for goal achieving.
Evidence from other contexts (e.g., intertemporal choice, [@Kable2007]) shows that subjective values (SVs) are attributed to the choice options on the basis of which the decision is made.
Research on ER choice has identified numerous factors that influence the choice of ER strategies, which can be seen as indirect evidence for factors influencing SVs. 
For example, it was shown that the intensity of a stimulus or situation plays a role in the choice [@Sheppes2011]. 
Higher intensity of the stimulus leads to a choice of rather disengaging strategies, like distraction [@Sheppes2011;@Sheppes2014].
Further influencing factors are for example extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Especially for effort, in our previous work we could show that the choice for an ER strategy is mainly influenced by effort [@Scheffel2021].
In this study, participants used the strategies distancing and suppression while inspecting emotional pictures.
Afterwards they could choose, which strategy they want to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
What has been missing in research on ER choice so far is information regarding the strategy *not* chosen.
People choose a strategy that they prefer, for different, relatively well-known reasons. 
However, nothing is revealed about the strategy that is not chosen.

<!-- JZ: Hier mal ein Vorschlag für eine andere Variante des oberen Absatzes, ohne inhaltlich was zu verändern: -->
The postulation of *adaptive* and *maladaptive* strategies was put into a new perspective with the concept of ER flexibility.
Similar to other psychological domains such as attention and goal pursuit, *maladaptive* now refers to inflexible strategy use or use of strategies that are hindering the achievement of goals [@Aldao2015].
In contrast, *adaptive* ER requires having a large repertoire of ER strategies to choose from [@Aldao2015] and choosing the strategy that is useful for goal achieving in a particular situation.
This greater ER variability has been shown to be related to reduced negative affect [@Blanke2020].
The process of choosing an ER strategy from one's own repertoire likely shares similarities with other contexts such as intertemporal choice, in which individuals assign subjective values to every choice option [@Kable2007].
Additionally, there are ER-specific influences on choice behaviour such as the intensity of the stimulus or situation, which leads to a choice of rather disengaging strategies like distraction, extrinsic motivation (e.g. monetary incentives), motivational determinants (i.e. hedonic regulatory goals), and effort [@Sheppes2014;@Scheffel2021].
Effort in particular appeared to be the main factor in ER choice behaviour in our previous work [@Scheffel2021].
In that study, participants used the strategies distancing and suppression while inspecting emotional pictures, and could choose which strategy they wanted to use again.
Participants tended to re-apply the strategy that was less effortful, even though it was not the most effective one for them - in this case: Suppression.
Interestingly, the choice was independent of self reported habitual use of suppression and reappraisal.
Research on ER choice has shown that individuals choose a strategy that they prefer for different, relatively well-known reasons.
However, nothing has been investigated regarding the strategy that is *not* chosen.

We assume that people choose the strategy that has the highest value for them at that moment.
The value is determined against the background of goal achievement in the specific situation: A strategy is highly valued if it facilitates goal achievement [@Aldao2015]. 
One certainly central goal is the regulation of negative affect.
A second, intrinsic and rather less obvious goal is the avoidance of effort [@Inzlicht2018].
When given the choice, most individuals prefer tasks that are less effortful [@Hull1943].
We assume that both aspects are set off against each other by individuals to determine individual subjective values (SVs) of ER strategies: A strategy is more valuable if it can reduce emotional arousal *and* is less effortful.
SVs of ER Strategies could be helpful to describe the ER repertoire [@Aldao2015] more comprehensively.
Depending on the flexibility of a person, different patterns of SVs could be conceivable: A person with high flexibility would show relatively high SVs for a number of strategies.
This would mean that all strategies are a good option for goal achievement.
A second person with less flexibilty, however, would show high SVs only for one strategy, or for no strategy at all.
This in turn would mean that no strategy is a good choice to achieve goals.

However, so far we have not seen any attempt in ER choice research to determine individual SVs of ER strategies.
To investigate this question, the individual subjective values of each strategy available for selection would have to be determined.
Promising approaches can be found in studies on difficulty levels of effortful cognitive tasks.  
Individual SVs of effortful cognitive tasks have been quantified using the Cognitive Effort Discounting Paradigm (COG-ED) [@Westbrook2013].

@@

In the original study by Westbrook et al. [-@Westbrook2013], cognitive load was varied using the *n*-back task, a working memory task that requires fast and accurate responses to sequentially presented stimuli. 
Participants had to decide whether they wanted to repeat a higher *n*-back level for a larger, fixed monetary reward, or a lower level for a smaller, varying reward. 
In the current study, we want to use this paradigm to determine SVs of ER strategies.
In doing so, we need to make an important change: We have to adapt the assumption that the easiest *n*-back level has the highest SV.
As we have shown in previous studies, there are large inter-individual differences in the preference and perceived subjective effort of ER strategies [@Scheffel2021].
Moreover, there is nothing like an objectively easiest ER strategy.
Therefore, we have to add an additional step, which preceeds the other steps and where the option with the higher subjective value is determined. 
In this step, the same monetary value (i.e., 1 EUR) is assigned to both options.
The assumption is that participants now choose the option that has the higher SV for them.
In the next step we return to the original paradigm.
The higher monetary value (i.e., 2 EUR) is assigned to the option that was not chosen in the first step and therefore is assumed to have the lower SV.
In the following steps, the lower value is changed in every iteration according to Westbrook et al. [-@Westbrook2013] until the indifference point is reached.
This procedure will be repeated until all strategies have been compared.
The SV of each strategy is calculated as the mean of this strategy's SV from all comparisons.
In case a participant has a clear preference for one strategy, the SV of this strategy will be 1.
But our paradigm can also account for the case that a person does not have a clear preference.
Then no SV will be 1, but still, the SVs of all strategies can be interpreted as absolute values and in relation to the other strategy's SVs (see figure 1).
Additionally, we will test our adapted paradigm in a *n*-back task and explore whether this paradigm can describe individuals that do not prefer the easiest *n*-back option (see Zerna et al., ...).
```{r fig1, echo = FALSE, message = FALSE, warning = FALSE, fig.cap = "Exemplary visualisation of two response patterns. In the top half, the person has a clear preference for one of the three strategies. In the lower half, they have no clear preference and therefore show an inconsistent response pattern. This pattern can also be represented by our paradigm."}
include_graphics(here("99_Thinktank","other","Paradigm_Scheme_T2.png" ))
```
## 1.2 The present study

The aim of the present study is to evaluate if this paradigm is suitable for determining SVs of ER strategies. 
We also want to find out whether the SVs are associated with subjective and physiological ER success, subjective effort, ER choice, and relevant personality traits.
We expect that (1) distancing and distraction lead to higher decrease in emotional arousal (subjective ratings, corrugator and levator activity) than suppression, (2a) people select the ER strategy that is less effortful if they have a choice, (2b) distancing is subjectively more effortful than distraction and suppression.
Regarding SVs of ER strategies we expect that (3a) people choose to re-apply the strategy with the highest SV, (3b) SVs of strategies are predicted by subjective arousal and levator and corrugator activity and subjective effort.
Regarding personality traits, we expect that (4a) self-regulation is associated with ER success and (4b) people with higher ER flexibility show no clearly preferred strategy in SVs. 
<!-- to specific ? to unspecific? -->
<!--JZ: Hier noch den Zsmh zwischen T1 und T2, oder?-->
